### 2021-09-19 paper/paper.tex
rename report

\newpage
\appendix
\section{A Technical Discussion of FCNs} \label{s:appendix-fcn}
We begin by introducing the notation\footnote{Note that some of the notation used in this work is not standard, but chosen on pedagogical grounds for better semantics (e.g. $ {\color{myMaroon} l} $ to index {\color{myMaroon} l}ayers, $ {\color{myMaroon} c} $ to index {\color{myMaroon} c}lasses, $ {\color{myMaroon} a} $ for {\color{myMaroon} a}ctivation value, etc...).} needed to describe a FCN:
\begin{itemize}

>>>>

\newpage
\appendix
\section{A More Technical Discussion of FCNs} \label{s:appendix-fcn}
We begin by introducing the notation\footnote{Note that some of the notation used in this work is not standard, but chosen on pedagogical grounds for better semantics (e.g. $ {\color{myMaroon} l} $ to index {\color{myMaroon} l}ayers, $ {\color{myMaroon} c} $ to index {\color{myMaroon} c}lasses, $ {\color{myMaroon} a} $ for {\color{myMaroon} a}ctivation value, etc...).} needed to describe a FCN:
\begin{itemize}
